An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-14 indicators/paper/paper.tex
Tweak forecasting text

\subsection{COVID-19 Forecasting Systems}

Since July 2020, Delphi has been regularly submitting short-term forecasts of
COVID-19 case and death incidence, at the state and county levels, to the
COVID-19 Forecast Hub \cite{ForecastHub}, under the name ``CMU-TimeSeries''.
Building, training, and deploying our forecasting models leverages much of the
infrastructure described in this paper (such as the COVIDcast API's \textit{as
  of} feature), and some of our forecasting models rely on auxiliary indicators
(such as survey-based and claims-based COVID-like illness indicators, described
below, which we have used in case forecasting).

>>>>

\subsection{COVID Forecasting}

Since July 2020, Delphi has been regularly submitting short-term forecasts of
COVID-19 case and death incidence, at the state and county levels, to the
COVID-19 Forecast Hub \cite{ForecastHub}, under the name ``CMU-TimeSeries''.  
The process of building, training, and deploying our forecasting models
leverages much of the infrastructure described in this paper (such as the
COVIDcast API's \textit{as of} feature), and some of our forecasting systems
rely on auxiliary indicators (such as survey-based and claims-based COVID-like 
illness signals, described below, which we have used in case forecasting).
